Process and merge data

### 2021-04-10 analysis/01_data-overview.Rmd
Include latent human rights measure

  tar_load(skeleton)
  tar_load(chaudhry_clean)
  tar_load(pts_clean)
  tar_load(killings_all)
  tar_load(vdem_clean)
  tar_load(wdi_clean)
  tar_load(un_pop)
  tar_load(un_gdp)
  tar_load(ucdp_prio_clean)

@@

>>>>

  tar_load(skeleton)
  tar_load(chaudhry_clean)
  tar_load(pts_clean)
  tar_load(latent_hr_clean)
  tar_load(killings_all)
  tar_load(vdem_clean)
  tar_load(wdi_clean)
  tar_load(un_pop)
  tar_load(un_gdp)
  tar_load(ucdp_prio_clean)

@@

## Latent Human Rights Protection Scores

We also use Chris Fariss's [Latent Human Rights Protection Scores](https://doi.org/10.7910/DVN/RQ85GK), which are estimates from fancy Bayesian models that capture a country's respect for physical integrity rights. We use the posterior mean of the latent variable from the model (θ), and we keep the standard deviation of θ just in case we want to fancier things in the future and incorporate the uncertainty of θ in the models. We rename θ to `latent_hr_mean`.

In this measure, high values represent strong respect for physical integrity rights:

```{r showh-lhr-min-max}
latent_hr_clean %>% 
  filter(latent_hr_mean == max(latent_hr_mean) | 
           latent_hr_mean == min(latent_hr_mean)) %>% 
  left_join(select(skeleton$skeleton_lookup, gwcode, country),
            by = "gwcode") %>% 
  select(country, everything())
```

```{r glimpse-lhr}
glimpse(latent_hr_clean)
```
